\documentclass[11pt,letterpaper]{article}

% Packages
\usepackage[margin=0.3in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}

% Colors
\definecolor{sectioncolor}{HTML}{333333}
\definecolor{linkcolor}{HTML}{0057B8}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor
}

% Section formatting
\titleformat{\section}
  {\normalfont\Large\bfseries\color{sectioncolor}}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{2pt}{5pt}

\setlength{\parindent}{0pt}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      #3 & #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\skill}[2]{
  \textbf{#1:} #2 \\
}

\begin{document}

% Header
\noindent
\begin{minipage}[c]{0.75\textwidth}
    {\huge \textbf{Aditya Khandelwal}} \\[4pt]
    Jaipur, Rajasthan $\cdot$ +91 9828460280 \\[2pt]
    \href{mailto:adityakhandelwal0271@gmail.com}{Email} $\cdot$
    \href{https://www.linkedin.com/in/nvmaditya/}{LinkedIn} $\cdot$
    \href{https://github.com/nvmaditya}{GitHub} $\cdot$
    \href{https://theadityakhandelwal.in/}{Portfolio}
\end{minipage}%

\vspace{2.5pt}

\section{PROFESSIONAL SUMMARY}
Execution-first CS undergraduate who builds working AI-powered systems end-to-end across any tech stack. Across 3 internships, built LLM extraction pipelines at Sentient Scripts, researched time series forecasting at Samsung R\&D, and developed real-time CV systems at Infosys. Independently built multi-agent (PromptGraph) and full-stack RAG (VectorLearn) systems. Uses AI as leverage to move fast and deliver outcomes.

\section{TECHNICAL SKILLS}
\skill{Languages}{Python, JavaScript, TypeScript, SQL}
\skill{AI / ML}{LangGraph, LangChain, OpenAI API, Groq API, Gemini API, RAG, FAISS, PyTorch, YOLOv8, OpenCV}
\skill{Backend}{FastAPI, REST APIs, SSE Streaming, Pydantic, asyncio, Microservices}
\skill{Full-Stack}{Next.js, React.js, Vite, Express.js}
\skill{Databases \& DevOps}{PostgreSQL, MySQL, SQLite, FAISS, Git, Docker, CI/CD, Linux}

\section{PROFESSIONAL EXPERIENCE}
\begin{itemize}[leftmargin=*]

\resumeSubheading
{AI Engineer Intern}{Aug 2025 -- Mar 2026}
{Sentient Scripts, Discovery Lab SRMIST}{}
\begin{itemize}[leftmargin=*]
    \item Built multi-source data aggregation pipelines in Python that ingested, normalized, and consolidated intelligence from 5+ external feeds for real-time monitoring and trend tracking.
    \item Developed an LLM-based extraction module that transformed unstructured text into structured domain-specific metadata, reducing manual extraction time by over 70\% and enabling automated cross-dataset correlation.
    \item Designed an end-to-end intelligence pipeline integrating scheduled data collection, LLM-driven correlation with Pydantic-validated output, and automated report generation, cutting turnaround from hours to minutes.
\end{itemize}

\resumeSubheading
{Research Intern}{Apr 2025 -- Jan 2026}
{Samsung R\&D Institute India Bangalore (Remote)}{}
\begin{itemize}[leftmargin=*]
    \item Benchmarked the TOTEM time series forecasting model with PyTorch across 4+ datasets and multiple forecasting horizons, producing comparative accuracy analyses against baseline transformer architectures.
    \item Identified tokenization and architecture design trade-offs that impacted long-horizon generalization, contributing findings to the team's ongoing model evaluation process.
\end{itemize}

\resumeSubheading
{Python Developer Intern}{Nov 2025 -- Jan 2026}
{Infosys Springboard (Remote)}{}
\begin{itemize}[leftmargin=*]
    \item Built a multi-zone real-time crowd counting system using YOLOv8 and OpenCV with Python multiprocessing to concurrently handle 4+ video streams, achieving measurable per-frame latency reduction.
    \item Designed a centralized monitoring dashboard with automated threshold-based alerting, eliminating manual stream supervision and reducing incident response time across all monitored zones.
\end{itemize}

\end{itemize}

\section{TECHNICAL PROJECTS}
\begin{itemize}[leftmargin=*]

\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{PromptGraph - Multi-Agent Prompt Architecture Generator \href{https://github.com/nvmaditya/PromptGraph}{[GitHub]}} & \\
  \textit{\small Tech Stack: Python, LangGraph, Groq API, Pydantic, FastAPI} & \\
\end{tabular*}\vspace{-5pt}
\begin{itemize}[leftmargin=*]
    \item Architected a 6-agent LangGraph StateGraph pipeline that converts natural language project ideas into structured prompt architectures and production-ready Python scaffolding in a single run.
    \item Implemented a 3-layer fault-tolerance system (Tenacity exponential backoff, rate limiting, schema self-healing) that reduced token consumption by $\sim$59\% via compact schema representation.
    \item Built a Critic-Refiner quality loop evaluating prompts across 5 dimensions; validated with a 190-test suite covering unit, integration, and live API regression.
\end{itemize}

\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{VectorLearn - Document Intelligence Platform \href{https://github.com/nvmaditya}{[GitHub]}} & \\
  \textit{\small Tech Stack: Python, FastAPI, React, Vite, TailwindCSS, FAISS, SQLite, Ollama, RAG} & \\
\end{tabular*}\vspace{-5pt}
\begin{itemize}[leftmargin=*]
    \item Built a full-stack AI tutoring platform with a RAG pipeline supporting multi-user document upload, isolated FAISS vector stores per user, and an SSE-streaming chat interface returning source-cited answers.
    \item Engineered a modular \texttt{docpipe} ingestion pipeline handling PDF extraction, recursive chunking, \texttt{bge-large} embeddings via Ollama, and per-user FAISS+SQLite indexing for accurate semantic retrieval.
\end{itemize}

\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{AI PPT Generator - Real-Time Presentation Deck Builder \href{https://github.com/nvmaditya}{[GitHub]}} & \\
  \textit{\small Tech Stack: Python, FastAPI, Groq API, Vite, JavaScript, SSE, pptxgenjs} & \\
\end{tabular*}\vspace{-5pt}
\begin{itemize}[leftmargin=*]
    \item Built a prompt-to-deck system powered by Groq API that streams slide content progressively via SSE with in-browser editing and reordering, cutting deck creation time to under 60 seconds.
    \item Designed a FastAPI backend with typed SSE event contracts (title/slide/done/error) and a Node.js \texttt{pptxgenjs} export script; supported configurable tone, slide count (5-20), and multi-language output.
\end{itemize}

\end{itemize}

\section{HACKATHONS \& ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Code Zero Hackathon - 2nd Place} & \textit{National Level} \\
\end{tabular*}\vspace{-5pt}
\begin{itemize}[leftmargin=*]
    \item Outperformed teams nationwide by designing and building a functional AI prototype under strict time constraints, demonstrating execution speed and problem-solving under pressure.
\end{itemize}
\end{itemize}

\section{EDUCATION}
\begin{itemize}[leftmargin=*]
\resumeSubheading
{SRM Institute of Science and Technology}{2023 -- 2027}
{B.Tech in Computer Science and Engineering}{CGPA: 8.91 / 10}
\resumeSubheading
{BVB Vidyashram}{}
{Senior Secondary (Class XII)}{82.80\%}
\end{itemize}

\end{document}