\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.3in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

\definecolor{sectioncolor}{HTML}{333333}
\definecolor{linkcolor}{HTML}{0057B8}

\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor
}

\titleformat{\section}
  {\normalfont\Large\bfseries\color{sectioncolor}}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{2pt}{5pt}

\setlength{\parindent}{0pt}

\newcommand{\resumeItem}[1]{\item{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      #3 & #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\skill}[2]{\textbf{#1:} #2 \\}

\begin{document}

\begin{center}
    {\huge \textbf{Aditya Khandelwal}} \\
    \vspace{5pt}
    Jaipur, Rajasthan $\cdot$ +91 9828460280 \\
    \href{mailto:adityakhandelwal0271@gmail.com}{Email} $\cdot$
    \href{https://www.linkedin.com/in/nvmaditya/}{LinkedIn} $\cdot$
    \href{https://github.com/nvmaditya}{GitHub} $\cdot$
    \href{https://theadityakhandelwal.in/}{Portfolio}
\end{center}

\section{PROFESSIONAL SUMMARY}
CS undergraduate with experience in data-driven systems, machine learning, and backend data pipelines using Python. Built end-to-end workflows involving data extraction, cleaning, transformation, and analysis to solve real-world problems. Experienced in exploratory data analysis, statistical modeling, and automation using Python (pandas, NumPy, scikit-learn) and SQL. Worked on time series forecasting and real-time computer vision systems.

\section{TECHNICAL SKILLS}
\skill{Languages}{Python, SQL, JavaScript, TypeScript}
\skill{Data Science}{Pandas, NumPy, Scikit-learn, Matplotlib, Plotly, EDA, Hypothesis Testing, Feature Engineering}
\skill{Machine Learning}{Supervised Learning, Time Series Forecasting, Model Evaluation, Deep Learning (PyTorch, YOLOv8)}
\skill{Data Engineering}{Data Pipelines, ETL, Data Cleaning, API Integration, Web Scraping}
\skill{Databases}{PostgreSQL, MySQL, NoSQL Basics}
\skill{Backend}{FastAPI, REST APIs, Automation Scripts}
\skill{Tools}{Excel, Git, Docker, Linux}

\section{PROFESSIONAL EXPERIENCE}
\begin{itemize}[leftmargin=*]

\resumeSubheading
{AI Engineer Intern}{Aug 2025 -- Mar 2026}
{Sentient Scripts, Discovery Lab SRMIST}{}
\begin{itemize}[leftmargin=*]
    \item Built multi-source data aggregation pipelines in Python that collected, normalized, and consolidated structured intelligence from external feeds for real-time monitoring and trend tracking.
    \item Developed an LLM-based information extraction module that processed unstructured text to identify and structure domain-specific technical metadata, enabling automated correlation across large datasets.
    \item Designed an end-to-end intelligence pipeline integrating scheduled data collection, LLM-driven correlation with structured output parsing (Pydantic), and automated report generation with trend visualizations.
\end{itemize}

\resumeSubheading
{Research Intern}{Apr 2025 -- Jan 2026}
{Samsung R\&D Institute India Bangalore (Remote)}{}
\begin{itemize}[leftmargin=*]
    \item Worked on time series forecasting using transformer-based models (TOTEM) in PyTorch across multiple datasets.
    \item Conducted comparative analysis of forecasting performance using different input representations and tokenization strategies.
    \item Evaluated model accuracy using statistical metrics and analyzed generalization across forecasting horizons.
\end{itemize}

\resumeSubheading
{Python Developer Intern}{Nov 2025 -- Jan 2026}
{Infosys Springboard (Remote)}{}
\begin{itemize}[leftmargin=*]
    \item Built a real-time crowd estimation system using YOLOv8 and OpenCV to generate time-series data from video streams.
    \item Processed and analyzed detection data to identify patterns and threshold-based anomalies.
    \item Optimized multiprocessing pipelines for efficient real-time data processing and reduced latency.
\end{itemize}

\end{itemize}

\section{TECHNICAL PROJECTS}
\begin{itemize}[leftmargin=*]

\item \textbf{Automatic Number Plate Recognition (ANPR) 
\href{https://github.com/nvmaditya/ANPR}{[GitHub]}} \\
\textit{\small Python, YOLOv8, EasyOCR, OpenCV, SORT}
\begin{itemize}[leftmargin=*]
    \item Trained a custom YOLOv8 license plate detector using Open Images dataset in YOLO format and exported optimized weights for deployment.
    \item Built an end-to-end ANPR pipeline combining vehicle detection, license plate localization, and OCR-based text extraction.
    \item Implemented multi-object tracking (SORT) to maintain vehicle identities across frames and improve OCR consistency.
    \item Designed both batch and real-time processing pipelines with CSV logging, interpolation of missing detections, and annotated video output.
\end{itemize}

\item \textbf{Real-Time Crowd Counting and Analysis 
\href{https://github.com/nvmaditya/CrowdCount}{[GitHub]}} \\
\textit{\small Python, YOLOv8, OpenCV, Multiprocessing}
\begin{itemize}[leftmargin=*]
    \item Developed a real-time crowd counting system using object detection to generate structured time-series data from video streams.
    \item Processed detection outputs to analyze crowd density patterns and threshold-based anomalies.
    \item Optimized concurrent video pipelines using multiprocessing for low-latency performance.
\end{itemize}

\item \textbf{PromptGraph -- Multi-Agent Pipeline Generator 
\href{https://github.com/nvmaditya/PromptGraph}{[GitHub]}} \\
\textit{\small Python, LangGraph, FastAPI, Pydantic}
\begin{itemize}[leftmargin=*]
    \item Built a multi-stage pipeline converting unstructured inputs into structured representations using LLMs.
    \item Designed schema validation and transformation layers using Pydantic for reliable data processing.
    \item Implemented retry, error handling, and structured output pipelines for robust automation workflows.
\end{itemize}

\end{itemize}

\section{HACKATHONS \& ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
\item Code Zero Hackathon -- 2nd Place (National Level)
\end{itemize}

\section{EDUCATION}
\begin{itemize}[leftmargin=*]
\resumeSubheading
{SRM Institute of Science and Technology}{2023 -- 2027}
{B.Tech in Computer Science and Engineering}{CGPA: 8.90}
\resumeSubheading
{BVB Vidyashram}{}
{Senior Secondary (Class XII)}{82.80\%}
\end{itemize}

\end{document}